Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-17 paper/sec-pileup.tex
More work in the PU section

{\bf add plots of these various distributions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \vspace{-1cm}
  \includegraphics[width=0.60\textwidth]{plots/pu-vs-nopu-comparison-d2.pdf}
  \caption{\small
    Comparison of the distribution of the $D_2^{(\beta)}$
    substructure variable, Eq.~(\ref{eq:d2}), for the
    boosted category in two cases: without PU, and
    with $\la n_{\rm PU}\ra=150$ PU events.
    %
    In the latter case, PU has been subtracted using
    {\tt SoftKiller}.
    %
    See text for more details.
}
\label{fig: pu-vs-nopu-comparison-d2}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \vspace{-1cm}
  \includegraphics[width=0.60\textwidth]{plots/pu-vs-nopu-comparison-d2.pdf}
  \caption{\small
    Comparison of the distribution of the $D_2^{(\beta)}$
    substructure variable, Eq.~(\ref{eq:d2}), for the
    boosted category in two cases: without PU, and
    with $\la n_{\rm PU}\ra=150$ PU events.
    %
    In the latter case, PU has been subtracted using
    {\tt SoftKiller}.
    %
    See text for more details.
}
\label{fig:pu-vs-nopu-comparison-d2}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

We now compare a number of signal distributions with
and without PU.
%
In Fig.~\ref{fig:m_H_PU} we show first of all the invariant mass distribution
of the leading and subleading Higgs candidates in the boosted
and resolved categories.
%
These distributions are plotted after the $b$-tagging,
before they are used as input to the MVA.
%
As we can see, in the boosted category, the residual effects of PU
after the SoftKiller subtraction are very mild in this
distribution.
%
The effects are more important for the resolved category, where PU
shifts the Higgs peak by am amount $\Delta m_h \simeq 5$ GeV.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \vspace{-1cm}
      \includegraphics[width=0.49\textwidth]{plots/m_H0_res_comp.pdf}
      \includegraphics[width=0.49\textwidth]{plots/m_H1_res_comp.pdf}
      \includegraphics[width=0.49\textwidth]{plots/m_H0_bst_comp.pdf}
      \includegraphics[width=0.49\textwidth]{plots/m_H1_bst_comp.pdf}
  \caption{\small
    Comparison of the invariant mass distributions of the leading (left plots)
    and subleading (right plots) Higgs candidates in the resolved
    (upper plots) and boosted (lower plots) categories,
    without PU and with $\la n_{PU}\ra=80$ subtracted with SoftKiller.
}
\label{fig:m_H_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
